The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Grammar

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solvers for all (competitive and non-competitive) division from
2015--2018.
We include solvers that were running hors concours (and hence non-competing
and ineligible to be recognized as official competition winners).
Non-com-petitive divisions use gray font.
Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
but non-competing solver $B$ actually ranked best if non-competing solvers
were taken into consideration.
Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.
Table cell colors (other than white) indicate the best competing sequential
solver performance; no cell color indicates that the best sequential solver
performance was by a non-competing solver and no competing solvers participated
in that division.
Full division rankings are available from the competition website.

>>>>

Tables~\ref{tab:winners-main}--\ref{tab:winners-unsat-core} show the
highest-ranked solvers for all (competitive and non-competitive) divisions from
2015--2018.
We include solvers that were running hors concours (and hence non-competing
and ineligible to be recognized as official competition winners).
Non-com-petitive divisions use gray font.
Entries $A [B]$ indicate that solver $A$ was the highest competing solver,
but non-competing solver $B$ actually ranked best if non-competing solvers
were taken into consideration.
Entries
$A/B$ indicate that solver~$A$ ranked first considering sequential
performance, while~$B$ ranked first considering parallel performance.
When the same solver ranked first in both, which is most often the
case, its name appears just once.
Table cell colors (other than white) indicate the best competing sequential
solver performance; no cell color indicates that the best sequential solver
performance was by a non-competing solver and no competing solvers participated
in that division.
Full division rankings are available from the competition website.
